Quantum Magic Games

### 2023-07-05 paper/main.tex
paper => typos

\begin{definition}[Magic Arrangement~\cite{arkhipov:2012}]\label{def:magic-arr}
  An arrangement is said magic its parity is \(-1\) and there exists
  a quantum realization of it.
\end{definition}

>>>>

\begin{definition}[Magic Arrangement~\cite{arkhipov:2012}]\label{def:magic-arr}
  An arrangement is said magic if its parity is \(-1\) and there exists
  a quantum realization of it.
\end{definition}
